---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(dygraphs)
```
# persephone

[![Travis-CI Build Status](https://travis-ci.org/statistikat/persephone.svg?branch=master)](https://travis-ci.org/statistikat/persephone)
[![](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![](https://img.shields.io/github/languages/code-size/statistikat/persephone.svg)](https://github.com/statistikat/persephone)
[![](https://img.shields.io/github/last-commit/statistikat/persephone.svg)](https://github.com/statistikat/persephone/commits/master)

This package is an object oriented wrapper around the R Package [RJDemetra], which performs
time series adjustments with the java library [JDemetra+]

## Installation

You can install the package directly from GitHub with

``` r
devtools::install_github("statistikat/persephone")
```

## Usage

Objects can be constructed with `x13Single$new` or `tramoseatsSingle$new`. Subseqentually, 
the `run` method runs the model and `output` gives access to the output object from 
`RJDemetra`. 

```{r}
library(RJDemetra)
library(persephone)

data("AirPassengers")

obj <- x13Single$new(AirPassengers)
plot(obj)
obj$run()
obj$output$regarima
AirPassengers
```


[RJDemetra]: https://github.com/nbbrd/rjdemetra
[JDemetra+]: https://github.com/jdemetra
