---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# persephone

This package is an object oriented wrapper around the R Package [RJDemetra], which performs
time series adjustments with the java library [JDemetra+]

## Installation

You can install the package directly from GitHub with

``` r
devtools::install_github("statistikat/persephone")
```

## Usage

Objects can be constructed with `x13Single$new` or `tramoseatsSingle$new`. Subseqentually, 
the `run` method runs the model and `output` gives access to the output object from 
`RJDemetra`. 

```{r}
library(RJDemetra)
library(persephone)

data(myseries)

obj <- x13Single$new(myseries)
invisible(
  obj$run()
)
obj$output$regarima
myseries
```


[RJDemetra]: https://github.com/nbbrd/rjdemetra
[JDemetra+]: https://github.com/jdemetra
