---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "90%"
)
```
# persephone

[![Travis-CI Build Status](https://img.shields.io/travis/statistikat/persephone.svg?logo=travis)](https://travis-ci.org/statistikat/persephone)
[![](https://img.shields.io/badge/lifecycle-experimental-orange.svg?logo=github)](https://www.tidyverse.org/lifecycle/#experimental)
[![](https://img.shields.io/github/languages/code-size/statistikat/persephone.svg?logo=github)](https://github.com/statistikat/persephone)
[![](https://img.shields.io/github/last-commit/statistikat/persephone.svg?logo=github)](https://github.com/statistikat/persephone/commits/master)
 [![Coverage status](https://coveralls.io/repos/github/statistikat/persephone/badge.svg)](https://coveralls.io/r/statistikat/persephone?branch=master&service=github)

This package is an object oriented wrapper around the R Package [RJDemetra], which performs
time series adjustments with the java library [JDemetra+]

## Installation

You can install the package directly from GitHub with

``` r
devtools::install_github("statistikat/persephone")
```

## Usage

Objects can be constructed with `x13Single$new` or `tramoseatsSingle$new`. Subseqentually, 
the `run` method runs the model and `output` gives access to the output object from 
`RJDemetra`. 

```{r, message = FALSE}
library(persephone)

obj <- x13Single$new(AirPassengers)
plot(obj)
```

The original output from [RJDemetra] can be inspected via the `output` field.

```{r}
obj$run()
obj$output$regarima
```

## Further reading

More information can be found on the [github-pages site] for persephone.

* The [plotting vignette] contains examples of interactive plots 
* An overview of the package is available in the [useR!2019 slides]

[RJDemetra]: https://github.com/nbbrd/rjdemetra
[JDemetra+]: https://github.com/jdemetra
[github-pages site]: https://statistikat.github.io/persephone/
[useR!2019 slides]: https://statistikat.github.io/persephone/articles/presentation_useR.pdf
[plotting vignette]: https://statistikat.github.io/persephone/articles/plotting.html
