---
title: "Hierarchical time series"
author: "Gregor de Cillia"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    df_print: kable
vignette: >
  %\VignetteIndexEntry{Hierarchical time series}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "95%"
)
```

Hierarchical time series are time series that can be divided into sub-series.
In `persephone`, such objects are created similar to a nested list. The
following example creates a series with two subseries `a` and `b`

```{r}
library(persephone)
hts <- per_hts(
  a = per_x13(AirPassengers),
  b = per_tramo(AirPassengers)
)
hts
```

If the `run()` method of `hts` is invoked, the following adjustments will be
made

* the aggregate series `a+b` is adjusted and the results are saved in
  `hts$output`.
* `a` is adjusted with `x13()`
* `b` is adjusted with `tramoseats()`

The results can be viewed as follows

```{r}
display_result <- function(ts) {
  window(ts, end = c(1949, 6))
}
hts$run()
display_result(hts$adjusted)
display_result(hts$components$a$adjusted)
display_result(hts$adjusted_indirect)
```

The last line displays the results of an indirect adjustment which amounts to
`a$adjusted` + `b$adjusted` in this case.

## Several levels of hierarchies

In case more hierarchy levels are introduced, the calls to `per_hts` can be
nested.

```{r}
hts_nested <- per_hts(
  hts = hts,
  hts_child = per_hts(
    a = per_x13(AirPassengers)
  ),
  b = per_tramo(AirPassengers)
)
hts_nested
```

As we can see, the runs of `hts` are available to this object.

## Iterating over the hierarchy tree

To iterate over all components of a `per_hts` object, the `iterate` method
can be used. It baehaves similar to `lapply`.

```{r}
hts_nested$run()
hts_nested$iterate(as_table = TRUE, function(obj) {
  list(mean = mean(obj$adjusted),
       var = sd(obj$adjusted))
})
```

```{r}
hts_nested$iterate(as_table = TRUE, persephone:::generateQrList)[, 1:9]
```

## setting options recursively

```{r}
hts_nested$set_options(spec = "RSA1", recursive = TRUE)

get_spec <- function(x) {
  list(spec = x$spec)
}

## check if options where applied correctly
hts_nested$iterate(as_table = TRUE, get_spec)

## modify options beginning from hts
hts$set_options(spec = "RSA0", recursive = TRUE)
hts_nested$iterate(as_table = TRUE, get_spec)

```

