---
title: "Plotting with persephone"
date: "`r Sys.Date()`"
#output: rmarkdown::html_vignette
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
vignette: >
  %\VignetteIndexEntry{Interactive vizualization of persephone objects}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "95%"
  #fig.width=9
)
```

Plot will look different depending on whetether the `run()` method was already 
called. When the plot is first run, the `output` field of the time series object
changes from `NULL` to the output object from `RDDemetra`. Therefore, forcasts
and other Plots are available.

# Default plot method

The default S3 generic `plot()` shows the time series with the `dygraphs` 
package. The result is a zoomable representation of the series.

```{r}
library(persephone)

obj <- perX13(AirPassengers, "RSA1")
plot(obj, drawPoints = TRUE)
```

In case the time series was already run, the plot will look slightly different
and also show a forecast.

```{r}
obj$run()
plot(obj, drawPoints=TRUE, showOutliers = FALSE)
```


# plotSeasIrrCal

Seasonal-, irreguar components can be visualized with `plotSeasIrrCal`.

```{r}
plotSeasIrrCal(obj)
```

# residual plot

`plotResiduals()` returns a `plotly` object.

```{r}
plotResiduals(obj, which="acf")
```
