---
title: "Persephone, Seasonal Adjustment with an Object-oriented Wrapper for RJDemetra"
author: "Angelika Meraner, Gregor de Cillia, Alexander Kowarik"
date: "`r Sys.Date()`"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{Persephone, Seasonal Adjustment with an Object-oriented Wrapper for RJDemetra}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The R-package `persephone` was developed and is still under development to enable easy processing of multiple time series during the production of seasonally adjusted estimates. 
It builds on top of `RJDemetra` (<https://github.com/jdemetra/rjdemetra>), an R interface to JDemetra+, and provides analytical tools such as interactive plots to support the SA expert. 
The package should make it easy to construct personalized dashboards containing selected plots and diagnostics and to produce a Eurostat-Quality-Report.
Furthermore it supports hierarchical time series and should enable the future development of diagnostics for direct vs indirect adjustment, e.g. by using some results from the Hackathon on RJDemetra in Frankfurt.

## Installation

The package can be installed from GitHub via 

```{r installation, eval = FALSE}
devtools::install_github("statistikat/persephone")
```

Optionally it can be installed including vignettes (needs prettydoc):

```{r installation2, eval = FALSE}
devtools::install_github("statistikat/persephone", build_vignettes = TRUE)
```


## Getting started: Constructing Objects


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## References
